---
title: "GCSE English and Maths Results"
author: "JEJ <br> James Jiang, Edan Marlow, Junlu Zheng" 
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
library(readr)
gcse2019 <- read_csv("gcse-english-and-maths-national-data-2019-20.csv")
View(gcse2019)
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```

class: inverse, center, middle

## Introduciton

---

# Introduction
- Research Question - What is the correlation between different groups of people and scoring 5 or above in GCSE English and maths? 


---



class: inverse, center, middle

# Variables 

---

# Variable that will use

- Ethnicity

- Gender

- FSM

- SEN_type

- SEN_grouping

- Religious_denominated

- Value


---

# Code

```{r boring-analysis}
# a boring analysis
gcse2019 %>%
  select(Value, Ethnicity, School_characteristic) %>%
  filter(Value != "!") %>%
  glimpse()

```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
    ggplot(gcse2019, mapping = aes(x = School_characteristic, fill = Ethnicity)) +
    geom_bar()+
    coord_flip()

```


---

## Plot and text

.pull-left[
- In each school sample, there are nearly equal numbers of each ethnicity, except for the “All” category, which is particularly large. So we can take a random sample of ethnicities and compare them, and they're relatively fair.
When Asian is filtered, the percentage of Asians who scored more than five was different in each kind of schools, with some schools having a particularly high percentage and others having a particularly low percentage. 

- When we pulled a random sample of ethnicities, such as Black, White, and others, the data showed that the percentage of people got fives concentrated at a higher value in "state-varied mainstream" than in any other kind of school. In a school of the "all-state-varied," the proportion of people who get a five is lower than in other schools.
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
    gcse2019 %>%
    filter(Ethnicity == "Asian", Value != "!") %>%
    ggplot(mapping = aes(x = School_characteristic, y = Value)) +
    geom_point() +
    coord_flip()

```
]

---

# Thanks!
