---
title: "GCSE English and Maths Results"
author: "JEJ <br> James Jiang, Edan Marlow, Junlu Zheng" 
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
library(readr)
gcse2019 <- read_csv("gcse-english-and-maths-national-data-2019-20.csv")
View(gcse2019)
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```

class: inverse, center, middle

## Introduciton

---

# Introduction
- Research Question - What is the correlation between different groups of people and scoring 5 or above in GCSE English and maths? 


---



class: inverse, center, middle

# Variables 

---

# Variable that will use

- Ethnicity

- Gender

- FSM

- SEN_type

- SEN_grouping

- Religious_denominated

- Value


---

# Code

```{r boring-analysis}
# a boring analysis
gcse2019 %>%
    ggplot(mapping = aes(x = School_characteristic, fill = Ethnicity)) +
    geom_bar()+
    coord_flip()

```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))


```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

